---
title: "Annex to the Google Maps Ranking - Proximity Study"
author: |
  | Lead: Chris Dreyer ([rankings.io](https://rankings.io/))
  | Support: François Delavy & Daniel Kupka ([frontpagedata.com](https://frontpagedata.com/))
date: "Last updated on `r Sys.Date()`"
output:
  html_document:
    theme: paper
    highlight: kate
    # code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: false
    keep_md: true # keep the intermediary files, including the plots as .png
editor_options: 
  chunk_output_type: console
---


<style>
.list-group-item.active, .list-group-item.active:hover, .list-group-item.active:focus {
background-color: #D21D5C;
border-color: #D21D5C;
}

body {
font-family: 'Alegreya Sans', sans-serif;
color: #333333;
font-size: 18px;
}

h1 {
font-weight: bold;
font-size: 28px;
}

h1.title {
font-size: 30px;
color: #D21D5C;
}

h2 {
font-size: 24px;
}

h3 {
font-size: 18px;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, 
                      fig.showtext = TRUE, 
                      # dpi = 700,
                      dev = "svg", # vectorized + decrease size of .html (hence loading time)
                      echo = FALSE # hide code
)

knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", small.mark = ",", scientific = F)
})

Sys.setlocale("LC_TIME", "C")
# extrafont::loadfonts(device = "win")
extrafont::loadfonts()

```


```{r prep}
# SETUP

## packages: remove or add your necessary packages

required_packages <- c("tidyverse", "extrafont", "here", "colorspace", "pdftools", "kableExtra", "ggrepel", "zoo")

for(i in required_packages) { 
  if(!require(i, character.only = T)) {
    
    #  if package is not existing, install then load the package
    install.packages(i, dependencies = T)
    require(i, character.only = T)
  }
}


## save plots?
# save <- TRUE
save <- FALSE

## quality of png's
dpi <- 750

## font adjust; please adjust to client´s website
#extrafont::loadfonts(device = "win", quiet = TRUE)
#font_add_google("Montserrat", "Montserrat")
# font_add_google("Overpass", "Overpass")
# font_add_google("Overpass Mono", "Overpass Mono")



## theme updates; please adjust to client´s website
#theme_set(ggthemes::theme_clean(base_size = 15))
theme_set(ggthemes::theme_clean(base_size = 12, base_family = "FiraSans-Regular"))


my_theme <- function(){
  theme(
    # plot.margin = margin(30, 30, 30, 30),
    plot.background = element_rect(color = "white", # the border
                                   fill = "white"),
    plot.title = element_text(size = 14),
    plot.title.position = "plot",
    plot.subtitle = element_text(size = 10),
    plot.caption = element_text(color = "grey40",
                                size = 9),
    plot.caption.position = "plot",
    axis.line.x = element_line(color = "black",
                               size = .8),
    axis.line.y = element_line(color = "black",
                               size = .8),
    axis.title.x = element_text(size = 11,
                                face = "bold"),
    axis.title.y = element_text(size = 11,
                                face = "bold"),
    axis.text = element_text(size = 9,
                             color = "black",
                             face = "bold"),
    axis.ticks = element_blank(),
    panel.grid.major.x = element_line(size = .6,
                                      color = "#eaeaea",
                                      linetype = "solid"),
    panel.grid.major.y = element_line(size = .6,
                                      color = "#eaeaea",
                                      linetype = "solid"),
    panel.grid.minor.x = element_line(size = .6,
                                      color = "#eaeaea",
                                      linetype = "solid"),
    panel.grid.minor.y = element_blank(),
    panel.spacing.x = unit(2, "lines"),
    panel.spacing.y = unit(1, "lines")
  )
}

## theme settings for flipped plots
theme_flip <-
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_line(size = .6,
                                          color = "#eaeaea"))

## theme settings for maps
theme_map <- 
  theme_void(base_family = "Montserrat") +
  theme(legend.direction = "horizontal",
        legend.box = "horizontal",
        legend.margin = margin(10, 10, 10, 10),
        legend.title = element_text(size = 17, 
                                    face = "bold"),
        legend.text = element_text(color = "grey33",
                                   size = 12),
        plot.margin = margin(15, 5, 15, 5),
        plot.title = element_text(face = "bold",
                                  size = 20,
                                  hjust = .5,
                                  margin = margin(30, 0, 10, 0)),
        plot.subtitle = element_text(face = "bold",
                                     color = "grey33",
                                     size = 17,
                                     hjust = .5,
                                     margin = margin(10, 0, -30, 0)),
        plot.caption = element_text(size = 14,
                                    color = "grey33",
                                    hjust = .97,
                                    margin = margin(-30, 0, 0, 0)))

## numeric format for labels
num_format <- scales::format_format(big.mark = ",", small.mark = ",", scientific = F)

## main colors rankings.io
r_col <- "#D21D5C"

# to be updated if/when needed:
# bl_col <- "#00d188"
# bl_dark <- darken(bl_col, .3, space = "HLS")
# 
# ## colors + labels for interval stripes
# int_cols <- c("#bce2d5", "#79d8b6", bl_col, "#009f66", "#006c45", "#003925")
# int_perc <- c("100%", "95%", "75%", "50%", "25%", "5%")
# 
# ## colors for degrees (Bachelors, Massters, Doctorate in reverse order)
# cols_degree <- c("#e64500", "#FFCC00", darken(bl_col, .1))
# 
# ## gradient colors for position
# colfunc <- colorRampPalette(c(bl_col, "#bce2d5"))
# pos_cols <- colfunc(10)
```


```{r} 

# DATA LOADING

samples <- rio::import(here::here("proc_data", "samples_50cities.rds")) %>%
  mutate(
    geodist_miles = round(geodist * 0.62137119224, 4), # the distance in American miles instead of km
    drop = -drop, # we want the drop to be negative
    # convert the city to factor and order by population:
    City = fct_relevel(City, 
                       levels = c(
                         "New-York",
                         "Los-Angeles",
                         "Chicago",
                         "Miami",
                         "Dallas",
                         "Philadelphia",
                         "Houston",
                         "Atlanta",
                         "Washington",
                         "Boston",
                         "Phoenix",
                         "Seattle",
                         "San-Francisco",
                         "Detroit",
                         "San-Diego",
                         "Minneapolis",
                         "Tampa",
                         "Denver",
                         "Brooklyn",
                         "Queens",
                         "Riverside",
                         "Baltimore",
                         "Las-Vegas",
                         "Portland",
                         "San-Antonio",
                         "St.-Louis",
                         "Sacramento",
                         "Orlando",
                         "San-Jose",
                         "Cleveland",
                         "Pittsburgh",
                         "Austin",
                         "Cincinnati",
                         "Kansas-City",
                         "Indianapolis",
                         "Columbus",
                         "Charlotte",
                         "Virginia-Beach",
                         "Bronx",
                         "Milwaukee",
                         "Providence",
                         "Jacksonville",
                         "Salt-Lake-City",
                         "Nashville",
                         "Richmond",
                         "Memphis",
                         "Raleigh",
                         "New-Orleans",
                         "Louisville",
                         "Oklahoma-City"
                       )),
    City = recode(City,
                  "New-York" = "New York",
                  "Los-Angeles" = "Los Angeles",
                  "San-Francisco" = "San Francisco",
                  "San-Diego" = "San Diego",
                  "Las-Vegas" = "Las Vegas",
                  "San-Antonio" = "San Antonio",
                  "St.-Louis" = "St. Louis",
                  "San-Jose" = "San Jose",
                  "Kansas-City" = "Kansas City",
                  "Virginia-Beach" = "Virginia Beach",
                  "Salt-Lake-City"= "Salt Lake City",
                  "New-Orleans" = "New Orleans",
                  "Oklahoma-City" = "Oklahoma City"
    )
  )

# # check how many samples in first mile:
# ten_miles_samples = c("11", "12", "13", "14", "15","16", "17", "18","19", "20")
# samples %>% filter(Sample %in% ten_miles_samples) %>% count(geodist_miles) %>% mutate(
#   rough_geodist = cut(geodist_miles, breaks = seq(0, max(samples$geodist_miles)+1), labels = FALSE), # bin by mile
#   rough_geodist = ifelse(is.na(rough_geodist), 0, rough_geodist) # the bin 0 is 0 instead of NA
# ) %>%
#   ungroup() %>%
#   group_by(rough_geodist) %>%
#   summarise(sum_n = sum(n)) %>%
#   View()
# 
# samples  %>% filter(Sample %in% ten_miles_samples) %>% filter(geodist_miles < 1, geodist_miles != 0) %>% count(Sample)



```


```{r}

# DATA PROCESSING
#   we need an easy way to plot the distance to origin for the plots.
#   so, we bin the distance by mile, and compute the average rank in a bin.
# we then create several tibbles, one with an average by city
# and another with an average by city and sample.

# method: because the geo distance varies, and is not the EXACT same
# btw cities and samples, we bin by mile to plot.

# we start by adding "bin" (rounding) the geographical distance:
samples <- samples %>% 
  mutate(
    rough_geodist = cut(geodist_miles, breaks = seq(0, max(samples$geodist_miles)+1), labels = FALSE), # bin by mile 
    rough_geodist = ifelse(is.na(rough_geodist), 0, rough_geodist), # the bin 0 is 0 instead of NA
    granular_geodist = cut(geodist_miles, breaks = seq(0, max(samples$geodist_miles)+1, 0.1), labels = FALSE)/10, # bin by 10th of a mile 
    granular_geodist = ifelse(is.na(granular_geodist), 0, granular_geodist), # the bin 0 is 0 instead of NA
    rank = ifelse(rank == 21, 25, rank) # we use 25 to code missing values, instead of 21 -> better visibility, better highlight of difference.
  ) %>%
  rowwise() %>%
  mutate(
    unique_sample = paste(as.character(City), Sample, collapse = "_") # a unique id
  ) %>%
  ungroup()


# a tibble with an average by city
avg_by_city <- samples %>%
  group_by(City, rough_geodist) %>%
  summarise(avg_drop = mean(drop),
            n_samples = n(),
            sd = sd(drop),
            avg_rank = mean(rank),
            n_samples_out_of_top20 = sum(rank > 20)
  ) %>%
  ungroup() %>%
  mutate(
    percentage_out_of_top20 = (n_samples_out_of_top20 / n_samples),
    # avg_rank = ifelse(avg_rank > 20, 25, avg_rank), # we do not force 25 to +20 averages
    seg_color = ifelse(avg_rank > 20, "orange", "black") # to color the +20 samples
  )

# a table to store the values of the last geodist -> used to put label at the end of lines
data_ends <- avg_by_city %>%
  group_by(City) %>%
  mutate(last_geodist = max(rough_geodist)) %>%
  ungroup() %>%
  filter(rough_geodist == last_geodist)


# a tibble with an average by city and sample
avg_by_city_and_firm <- samples %>%
  group_by(City, Sample, rough_geodist) %>%
  summarise(avg_drop = mean(drop),
            avg_rank = mean(rank),
            n_samples = n(),
            n_samples_out_of_top20 = sum(rank > 20)
  ) %>%
  ungroup() %>%
  mutate(
    percentage_out_of_top20 = (n_samples_out_of_top20 / n_samples),
    # avg_rank = ifelse(avg_rank > 20, 25, avg_rank), # we do not force 25 to +20 averages
    seg_color = ifelse(avg_rank > 20, "orange", "black") # to color the +20 samples
  ) %>%
  rowwise() %>%
  mutate(
    unique_sample = paste(as.character(City), Sample, collapse = "_") # a unique id
  ) %>%
  ungroup()


# a tibble with an average by sample, regardless of city
avg_by_firm <- samples %>%
  group_by(unique_sample, rough_geodist) %>%
  summarise(avg_drop = mean(drop),
            n_samples = n(),
            sd = sd(drop),
            avg_rank = mean(rank),
            n_samples_out_of_top20 = sum(rank > 20)
  ) %>%
  ungroup() %>%
  mutate(
    percentage_out_of_top20 = (n_samples_out_of_top20 / n_samples),
    # avg_rank = ifelse(avg_rank > 20, 25, avg_rank), # we do not force 25 to +20 averages
    seg_color = ifelse(avg_rank > 20, "orange", "black") # to color the +20 samples
  )


# a tibble with a granularity of tenth of a mile:
# a tibble with an average by city and sample
avg_by_city_and_firm_granular <- samples %>%
  group_by(City, Sample, unique_sample, granular_geodist) %>%
  summarise(avg_drop = mean(drop),
            avg_rank = mean(rank),
            n_samples = n(),
            n_samples_out_of_top20 = sum(rank > 20)
  ) %>%
  ungroup() %>%
  mutate(
    percentage_out_of_top20 = (n_samples_out_of_top20 / n_samples),
    # avg_rank = ifelse(avg_rank > 20, 25, avg_rank), # we do not force 25 to +20 averages
    seg_color = ifelse(avg_rank > 20, "orange", "black") # to color the +20 samples
  ) %>%
  rowwise() %>%
  mutate(
    unique_sample = paste(as.character(City), Sample, collapse = "_") # a unique id
  ) %>%
  ungroup()

```

This is an annex to the [Google Maps Ranking - Proximity Study](https://frontpagedata.com/google-maps-proximity).  

# 10-Mile Grids for All Cities

We reproduced the Local Falcon grids with heat maps. Each tile is the rank of the law firm observed by Local Falcon on the 15x15 grid centered at the firm's location. The grids measure 10 miles by 10 miles. The data used to draw these grids can be found [here](https://docs.google.com/spreadsheets/d/1uOKfBcs_RgAxRf8fAlhmH8f5VLzPtf1t7enPWVT1mnM/edit?usp=sharing).   

Legend:  

```{r fig.align='center', fig.height=4.5, out.width='55%'}

normalize_10miles <- function(x){
  # min-max norm. btw 0 and 1
  return(round((x - min(x)) / (max(x) - min(x)), 3))
}

normalize_5miles <- function(x){
  # min-max norm. btw 0 and 0.5
  return(round((x - min(x)) * 0.5 / (max(x) - min(x)), 3))
}

to_plot_heatmap <- samples %>% select(City, Sample, rank, Latitude, Longitude) %>%
  filter(City == "Miami", Sample == "12") %>%
  mutate(
    rank_label = as.character(rank),
    rank_label = ifelse(rank_label == 25, "20+", rank_label),
    rank = ifelse(rank == 25, NA, rank),
  ) %>%
  group_by(Sample) %>%
  mutate( # need to normalize location else cannot facet them (not same axis)
    Long_norm = as.factor(normalize_10miles(Longitude)),
    Lat_norm = as.factor(normalize_10miles(Latitude))
  ) %>%
  ungroup()

ggplot(data = to_plot_heatmap,
       aes(x = Long_norm, y = Lat_norm, fill = rank) ) +
  geom_tile(show.legend = FALSE) +
  geom_text(aes(label = rank_label)) +
  scale_fill_gradient(low = "#005470", high = "#F3E5C9", na.value = "#ff8989", guide = FALSE) +
  coord_equal() + # force square tiles
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(), axis.ticks.x = element_blank(),
        panel.border=element_blank()) +
  theme_void()
# theme(panel.grid.major.x = element_blank())


```

```{r}
# a function to plot the heatmaps of all cities
plot_heatmap_20 <- function(Data, City_of_Choice, ten_miles_samples){
  Data %>% select(City, Sample, rank, Latitude, Longitude) %>%
    filter(City == City_of_Choice) %>%
    mutate(
      rank_label = as.character(rank),
      rank_label = ifelse(rank_label == 25, "20+", rank_label),
      rank = ifelse(rank == 25, NA, rank),
    ) %>%
    group_by(Sample) %>%
    mutate( # for now, we treat them the same, then just show the 10-mile radius samples
      Long_norm = ifelse(Sample %in% ten_miles_samples, 
                         as.factor(normalize_10miles(Longitude)),
                         as.factor(normalize_10miles(Longitude))),
      Lat_norm = ifelse(Sample %in% ten_miles_samples, 
                        as.factor(normalize_10miles(Latitude)),
                        as.factor(normalize_10miles(Latitude)))
    ) %>%
    ungroup() %>%
    filter(Sample %in% ten_miles_samples) %>%
    #plot:
    ggplot(aes(x = Long_norm, y = Lat_norm, fill = rank, label = rank_label) ) +
    facet_wrap(vars(Sample), ncol = 5)  +
    geom_tile(show.legend = FALSE) +
    scale_fill_gradient(low = "#005470", high = "#F3E5C9", na.value = "#ff8989", guide = FALSE) +
    coord_equal() + # force square tiles
    theme_void() +
    theme(
      panel.spacing.x = unit(0.01, "lines"), # less space around plots
      panel.spacing.y = unit(0.1, "lines"),
    )
}

# defining the size of the heatmaps:
hheight = 4
hwidth = '60%'

```

The visualizations below show the grids for the 20 samples with a 10-mile radius in each city.  

### New York

```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(11,30)) # says, for this city, which are the 10-mile samples
plot_heatmap_20(samples, "New York", ten_miles_samples)

```

### Los Angeles

```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(11,30)) # says, for this city, which are the 10-mile samples
plot_heatmap_20(samples, "Los Angeles", ten_miles_samples)

```

### Chicago

```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(11,30)) # says, for this city, which are the 10-mile samples
plot_heatmap_20(samples, "Chicago", ten_miles_samples)

```

### Miami

```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(11,30)) # says, for this city, which are the 10-mile samples
plot_heatmap_20(samples, "Miami", ten_miles_samples)

```

### Dallas

```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(11,30)) # says, for this city, which are the 10-mile samples
plot_heatmap_20(samples, "Dallas", ten_miles_samples)

```


### Philadelphia

```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(11,30)) # says, for this city, which are the 10-mile samples
plot_heatmap_20(samples, "Philadelphia", ten_miles_samples)

```

### Houston

```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(11,30)) # says, for this city, which are the 10-mile samples
plot_heatmap_20(samples, "Houston", ten_miles_samples)

```

### Atlanta

```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(11,30)) # says, for this city, which are the 10-mile samples
plot_heatmap_20(samples, "Atlanta", ten_miles_samples)

```

### Washington

```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(11,30)) # says, for this city, which are the 10-mile samples
plot_heatmap_20(samples, "Washington", ten_miles_samples)

```

### Boston

```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(11,30)) # says, for this city, which are the 10-mile samples
plot_heatmap_20(samples, "Boston", ten_miles_samples)

```

### Phoenix
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Phoenix", ten_miles_samples)

```

### Seattle
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Seattle", ten_miles_samples)

```

### San Francisco
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "San Francisco", ten_miles_samples)

```

### Detroit
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Detroit", ten_miles_samples)

```

### San Diego
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "San Diego", ten_miles_samples)

```

### Minneapolis
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Minneapolis", ten_miles_samples)

```

### Tampa
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Tampa", ten_miles_samples)

```

### Denver
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Denver", ten_miles_samples)

```

### Brooklyn
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Brooklyn", ten_miles_samples)

```

### Queens
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Queens", ten_miles_samples)

```

### Riverside
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Riverside", ten_miles_samples)

```

### Baltimore
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Baltimore", ten_miles_samples)

```

### Las Vegas
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Las Vegas", ten_miles_samples)

```

### Portland
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Portland", ten_miles_samples)

```

### San Antonio
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "San Antonio", ten_miles_samples)

```

### St. Louis
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "St. Louis", ten_miles_samples)

```

### Sacramento
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Sacramento", ten_miles_samples)

```

### Orlando
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Orlando", ten_miles_samples)

```

### San Jose
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "San Jose", ten_miles_samples)

```

### Cleveland
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Cleveland", ten_miles_samples)

```

### Pittsburgh
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Pittsburgh", ten_miles_samples)

```

### Austin
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Austin", ten_miles_samples)

```

### Cincinnati
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Cincinnati", ten_miles_samples)

```

### Kansas City
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Kansas City", ten_miles_samples)

```

### Indianapolis
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Indianapolis", ten_miles_samples)

```

### Columbus
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Columbus", ten_miles_samples)

```

### Charlotte
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Charlotte", ten_miles_samples)

```

### Virginia Beach
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Virginia Beach", ten_miles_samples)

```

### Bronx
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Bronx", ten_miles_samples)

```

### Milwaukee
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Milwaukee", ten_miles_samples)

```

### Providence
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Providence", ten_miles_samples)

```

### Jacksonville
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Jacksonville", ten_miles_samples)

```

### Salt Lake City
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Salt Lake City", ten_miles_samples)

```

### Nashville
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Nashville", ten_miles_samples)

```

### Richmond
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Richmond", ten_miles_samples)

```

### Memphis
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Memphis", ten_miles_samples)

```

### Raleigh
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Raleigh", ten_miles_samples)

```

### New Orleans
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Portland", ten_miles_samples)

```

### Louisville
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Louisville", ten_miles_samples)

```

### Oklahoma City
```{r fig.align='center', fig.height=hheight, out.width=hwidth}

ten_miles_samples <- as.character(seq(1,20)) # says, for this city, which are the 10-mile samples
ten_miles_samples <- stringr::str_pad(ten_miles_samples, 2, side = "left", pad = "0")
plot_heatmap_20(samples, "Oklahoma City", ten_miles_samples)

```




